Roster Review (Generic)

### 2019-08-09 rosterReview_generic.Rmd
Latest rosters

```{r ros_team_rankings}
rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  mutate(zar = round(zar,2)) %>% 
  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
  geom_point(aes(text=name_full)) +
  facet_wrap(~ team) -> team_pos_adj

>>>>

```{r ros_team_rankings}
# TODO adjust for DL
rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  mutate(zar = round(zar,2)) %>% 
  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
  geom_point(aes(text=name_full)) +
  facet_wrap(~ team) -> team_pos_adj
